Summary Tables

### 2020-02-26 summary_tables_outcomes.Rmd
Scale true distance to year (by 52)
Write long form, interactive and static plots of whw

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(DT)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

```{r whw_for_all_cs}

@@

@@

for (cs in names(all_whw)){
  # cs <- 'Baseline'

@@

   #var <- scen_lt %>% filter(scen_name == cs) %>% select(val) %>% as.character()

@@

@@

      td4[, 2] <- round((td4[,3] / ( td4[,2] )) * 100000, 4)
      # / sum(io[[city]]$demographic$population, na.rm = T)

>>>>

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(DT)
library(ggplot2)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

```{r whw_for_all_cs, fig.width=7, fig.height=4, echo=FALSE}

@@

file_list <- list()

@@

for (cs in names(all_whw)){
  # cs <- names(all_whw)[1]

@@

   backup_td <- td

@@

   colnames(td) = gsub("auto_rickshaw", "ar", colnames(td))

   whw_lng <- reshape2::melt(td)

   col_split <- stringr::str_split(whw_lng$variable, "_", simplify = TRUE, n = 2)

   whw_lng <- cbind(whw_lng, col_split)
   names(whw_lng)[4] <- 'strike_mode'
   names(whw_lng)[5] <- 'city'
   whw_lng <- whw_lng %>% dplyr::select(-variable)
   whw_lng <- whw_lng %>% dplyr::filter(strike_mode != "rowSum")
   whw_lng <- whw_lng %>% rename(str_mode = mode, cas_mode = strike_mode)

   whw_lng$str_mode <- factor(whw_lng$str_mode, levels = unique(whw_lng$str_mode))

   qualified_scen_name <- 'Bus'
   scen <- 'Scenario'

   if (cs == 'bl'){
     qualified_scen_name <- 'Baseline'
     scen <- ''
   }else if(cs == "w_sc"){
     qualified_scen_name <- 'Walking'
   }else if(cs == "bi_sc"){
     qualified_scen_name <- 'Bicycle'
   }else if(cs == "car_sc"){
     qualified_scen_name <- 'Car'
   }else if(cs == "mc_sc"){
     qualified_scen_name <- 'Motorcyle'
   }

   readr::write_csv(whw_lng, paste0('results/multi_city/whw_matrices/whw_lng_', cs, '.csv'))

   f <- ggplot(data = whw_lng) +
     aes(x = str_mode, fill = cas_mode, weight = value) +
     geom_bar(position = "stack") +
     scale_fill_brewer(palette = "Dark2") +
     labs(x = "Strike Mode", y = "# of incidents", title = paste("WHW - ", qualified_scen_name, scen)) +
     coord_flip() +
     facet_wrap(vars(city), scales = "free_y")

   file_list[[cs]] <- f

   ggsave(f, file = paste0("results/multi_city/whw_matrices/plots/whw_", cs,".png"), limitsize = F, dpi = 300, scale = 1.5)

   d <- paste0("results/multi_city/whw_matrices/interactive_plots/whw_", cs,".html")

   htmlwidgets::saveWidget(plotly::ggplotly(f), file.path(normalizePath(dirname(d)), basename(d)))
  #ggsave(f, file=paste0("results/multi_city/whw_matrices/whw_", cs,".png"), width = 14, height = 10, units = "cm")

@@

      td4[, 2] <- round((td4[,3] / ( td4[,2] * 52)) * 100000, 4)
      # / sum(io[[city]]$demographic$population, na.rm = T)
